\documentclass{letter}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\usepackage[margin=1in]{geometry}

\begin{document}

\begin{letter}{Schibsted Media\\
Stockholm, Sweden}

\opening{Dear Hiring Team,}

I am excited to apply for the Data Engineer position at Schibsted Media. With nearly 9 years of experience in software development and a strong background in building data-intensive applications, I am confident that my skills align closely with your needs for this role.

At \textbf{Weavler AB}, I extensively used and fully managed AWS services to develop a user-friendly e-commerce platform. I leveraged AWS to implement server-side rendering for improved SEO and integrated services like Slack bots and PayPal for enhanced functionality. This hands-on experience with AWS has given me a deep understanding of cloud solutions, which is directly applicable to the Data Platform team's work in developing and maintaining scalable applications on cloud platforms.

At \textbf{Oneflow AB}, while my opportunities to work with AWS were limited, I focused on building a dashboard of statistics highlighting contract statuses and signing rates over selectable time periods. I created BI queries to monitor integration performance and integrated user metrics tools like Appcues. These projects honed my ability to design and implement highly scalable applications and data pipelines, ensuring smooth and continuous operations—key responsibilities within the Data Platform team at Schibsted Media.

During my time at \textbf{Bumbee Labs}, I developed and maintained a data-intensive full-stack application. I managed and processed large datasets with MongoDB, optimized performance on Heroku, and enhanced the dashboard application using AngularJS and Python. This role reinforced my proficiency in Python and my understanding of data-intensive systems, essential for maintaining and optimizing data pipelines.

I have familiarity with CI/CD pipelines and infrastructure-as-code tools like Terraform, having completed the \textit{HashiCorp Terraform Associate} course. Additionally, my Master's degree in Computer Science from \textbf{Uppsala University}, where I focused on data mining, machine learning, and distributed systems, has provided me with a solid foundation in quantitative fields relevant to this role.

I am fluent in English and have strong communication skills, which have been essential in collaborating with cross-functional teams and assisting internal customers in using platforms effectively. I am also accustomed to working in agile environments, often in pairs or small groups, to deliver features efficiently.

I am enthusiastic about the opportunity to contribute to Schibsted Media's mission of establishing itself as a data-driven pioneer. The prospect of working on Pulse and developing a new data platform using the latest data technologies to serve billions of events daily is particularly exciting to me.

Thank you for considering my application. I look forward to the opportunity to discuss how my background and skills can support Schibsted Media's goals.

\closing{Warm regards,\\[2ex]
Peramanathan Sathyamoorthy}

\end{letter}

\end{document}