\documentclass{letter}
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}

\begin{document}

\begin{letter}{Schibsted Marketplaces\\
Stockholm, Sweden}

\opening{Dear Hiring Team,}

I am excited to apply for the Data Engineer position within Schibsted Marketplaces' Sales Insights department. With nearly 9 years of experience in software development and a strong background in building data-intensive applications, I am confident that my skills align closely with your needs for this role. The opportunity to shape data architecture and lead technical initiatives that drive commercial decisions is particularly appealing to me.

At \textbf{Oneflow AB}, I played a key role in developing dashboards that highlighted contract statuses and signing rates over selectable periods. I created BI queries to monitor integration performance and integrated user metrics tools like \textbf{Appcues}. These projects honed my proficiency in \textbf{Python} and advanced \textbf{SQL}, including performance tuning and optimization. Additionally, I co-founded the \textbf{Integration Team}, establishing key processes for scalability and integrating our platform with third-party services like \textbf{HubSpot} and \textbf{SuperOffice}, which required integrating data from various APIs and third-party sources.

During my time at \textbf{Bumbee Labs}, I developed and maintained a data-intensive full-stack application. I managed and processed large datasets with \textbf{MongoDB}, and enhanced the dashboard application using \textbf{AngularJS} and \textbf{Python}. This experience reinforced my understanding of data modeling techniques, data governance, and data quality management.

I have academic and personal exploration of \textbf{ETL/ELT processes}, though not with the exact tools mentioned. This exploration has given me a solid understanding of transforming data and managing data pipelines, which I am eager to apply and expand upon in a professional setting. My familiarity with \textbf{CI/CD pipelines} and \textbf{DevOps practices} is supported by completing the \textit{HashiCorp Terraform Associate} course. While at \textbf{Weavler AB}, I extensively used \textbf{AWS} services and implemented server-side rendering for improved SEO, showcasing my ability to work with cloud platforms and integrate data from various sources.

In leadership roles, I have mentored and guided team members, fostering a culture of continuous learning and growth. As an \textbf{Engineering Team Lead} at \textbf{Oneflow AB}, I led a self-organizing team through Agile methodologies, increasing productivity and ownership.

Holding a Master's degree in Computer Science from \textbf{Uppsala University}, I have a solid foundation in data mining, machine learning, and software engineering. This academic background, combined with my professional experience, equips me to take ownership of the Sales Insights' data architecture, ensuring scalability, reliability, and performance.

I am enthusiastic about the prospect of collaborating with cross-functional teams to deliver actionable insights and drive innovation within Schibsted Marketplaces. I believe my skills and experience make me a strong fit for this role, and I am eager to contribute to your mission of enhancing market presence and optimizing sales performance.

Thank you for considering my application. I look forward to the opportunity to discuss how my background and skills can support Schibsted Marketplaces' goals.

\closing{Warm regards,\\[2ex]
Peramanathan Sathyamoorthy}

\end{letter}

\end{document}
