\documentclass{letter}
\usepackage[utf8]{inputenc}
\usepackage[a4paper, margin=1in]{geometry}


\begin{document}

\begin{letter}{Schibsted Media\\
Stockholm, Sweden}

\opening{Dear Hiring Team,}

I am excited to apply for the Full Stack Engineer position with a strong AI focus within Schibsted Media's Shared Products \& Platforms (SPP) team.
This role perfectly aligns with my nearly 9 years of experience in full stack development and my passion for integrating AI solutions to enhance user experiences.
Schibsted's commitment to advancing editorial workflows through AI-driven tools resonates deeply with my dedication to leveraging technology to empower users and transform industries.

At Oneflow AB, I have cultivated a strong background in full stack development, specializing in JavaScript, TypeScript, React.js, and Python.
As a Full Stack Integration Engineer, I co-founded the Integration Team, where I established key processes for scalability and integrated our platform with various third-party services like HubSpot and SuperOffice.
By contributing to the development of our Public API and creating robust integration solutions, I gained valuable experience in building scalable systems and facilitating seamless data flow between platforms.
This experience is directly applicable to SPP's mission of integrating and scaling AI-powered services across editorial tools like Create CMS, as it requires a deep understanding of system integration, scalability, and collaborative development across diverse teams.

Earlier in my career, as part of a task force responding to emerging competition, I collaborated closely with another developer to lay the foundational work for a JSON-based rich text editor.
We tackled complex challenges by innovating solutions that made the editor stable and extensible, ultimately improving user satisfaction by 60\%.
This hands-on experience in developing scalable, user-centric solutions has equipped me with the skills to contribute effectively to your AI initiatives.

While my recent professional roles have focused more on full stack development, I have remained deeply engaged with AI technologies.
Over the past two years, I have pursued personal projects and continuous learning to stay at the forefront of AI advancements.
I have hands-on experience integrating AI models into web applications and have explored NLP techniques using models like LLaMA.
My recent completion of courses such as "Build LLM Apps with LangChain.js" and "LangChain Chat with Your Data" reflects my commitment to applying AI in practical settings.

My academic background further supports my capabilities for this role.
I hold a Master's degree in Computer Science from Uppsala University, where I built a strong foundation in machine learning through courses like Data Mining, Machine Learning, and Computer Assisted Image Analysis.
My thesis focused on enabling energy-efficient data communication through participatory sensing and mobile cloud, highlighting my ability to tackle complex technical challenges.

I am confident that my full stack expertise, combined with my proactive engagement in AI technologies, aligns well with Schibsted Media's vision for transforming editorial products.
I am eager to bring my experience and enthusiasm to your team and contribute to the innovative work being done at SPP.

Thank you for considering my application. I look forward to the opportunity to discuss how my background and skills can support Schibsted Media's goals.

\closing{Warm regards,\\ Peramanathan Sathyamoorthy}

\end{letter}

\end{document}
