%%%%% SECOND PAGE %%%%%
\newpage
\begin{minipage}[t]{0.29\textwidth} %% Left column -- outer definition
%  Left column -- top dark rectangle
% \colorbox{cvblue}{\begin{minipage}[t][5mm][t]{\textwidth}\null\hfill\null\end{minipage}}
% \colorbox{cvblue!90}
% {\begin{minipage}
%   [t][5mm][t]{\textwidth}\null\hfill\null
%   \raggedright
% \end{minipage}}

% \vspace{-0.3ex} % Eliminates the small gap
\colorbox{cvblue!90}
{\color{white}  %% LEFT BOX
  \kern0.09\textwidth\relax % Left margin provided explicitly
  \begin{minipage}[t][293mm][t]{0.82\textwidth}
  \raggedright
  \vspace*{2.5ex}

  \Large
  \headleft{Familiar Technologies}
  \begin{itemize}
      \item \textbf{AGI \& Infra}(New): LangChainjs, LLMs, Terraform, AWS SageMaker, AWS Bedrock
      \item \textbf{Workflow}: Graphite (Stacking PRs)
      \item \textbf{Fullstack}: Remix, Nextjs, Astro, Solid-start
      \item \textbf{Languages}: C, C++, Java, R, Erlang, Rust, Elixir
      \item \textbf{Data Science \& ML}: R, Python, NumPy, Panda, Scikit-learn
      \item \textbf{Front-End tools}: Esbuild, Vitejs
      \item \textbf{API Frameworks}: Django, Flask, Eve
      \item \textbf{Databases}: MySQL, Postgres, MongoDB
      \item \textbf{Deployment}: AWS (EC2, S3, IAM, ELB), Heroku, Netlify, Vercel, Fly.io
      \item \textbf{Miscellaneous}: Data Visualization, KPI Implementation, SEO Optimization, Accessibility Compliance, Speech Recognition, Chat Bot Development
  \end{itemize}

  \Large
  \headleft{Education}
  \Large
  \textbf{Master of Science in Computer Science}, \textit{Uppsala University (2010 - 2016)}\\
  \vspace{0.5em}
  \textbf{Master of Science in Operations Research and Computer Applications}, \textit{National Institute of Technology, Tiruchirappalli, Tamilnadu, India (2007 - 2009)}\\
  \vspace{0.5em}
  \textbf{Bachelor of Science in Mathematics}, \textit{Kadhir Mohideen College, Affiliated to Tiruchirappalli Bharathidasan University, Adirampattinam, Thanjavur, Tamilnadu, India (2004 - 2007)}\\

  \Large
  \headleft{REFERENCES}
  \vspace{0.5em}
  \Large
  \noindent
  \textbf{References available upon request}

  \end{minipage}
  \kern0.09\textwidth\relax%%Right margin provided explicitly to stretch the colourbox
}

\end{minipage}
% Right column
\hskip2.5em% Left margin for the white area
\begin{minipage}[t]{0.61\textwidth}
\setlength{\parskip}{1ex}% Adds spaces between paragraphs; use \\ to add new lines without this space. Shrink this amount to fit more data vertically

\vspace{1ex}

\Large
\headright{Experience}
\vspace{0.5em}
\Large
\noindent
\textbf{Oneflow AB} \hfill Stockholm, Sweden\\
\textit{Full Stack Integration Engineer (31 months)} \hfill March 2019 - September 2022
\begin{itemize}
\setlength{\itemsep}{0.5em}
    \item \textbf{Established the Integration Team} from the ground up, creating foundational processes and best practices for long-term scalability, while strategically aligning integration solutions with business needs.
    \item \textbf{Designed multi-client applications} with Python and React.js, facilitating seamless integrations with platforms like HubSpot and SuperOffice, expanding Oneflow’s reach and interoperability.
    Helped Microsoft Dynamics and Salesforce Development with reviews and frontend decision making.
    Built connector application extensions for the CRM integrations and Teamtailor
    \item \textbf{Stabilized and enhanced the Public API}, which enabled a robust third-party integration ecosystem, contributing to client satisfaction and platform versatility.
\end{itemize}
\vspace{0.2em}
\textbf{Tools Used}: \textit{Python, Reactjs, CRMs (HubSpot, SuperOffice, Microsoft Dynamics, Salesforce), Connexion, Integrations}

\vspace{1em}

\noindent
\textbf{Oneflow AB} \hfill Stockholm, Sweden\\
\textit{JavaScript Developer(23 months)} \hfill April 2017 - February 2019
\begin{itemize}
\setlength{\itemsep}{0.5em}
    \item \textbf{Innovatively Integrated React Router into a Backbone.js-based client} to build Identity and Access Management, facilitate faster prototyping cross-linked user management and efficient testing.
    \item \textbf{Optimized CI build processes}, reducing build times by 40\%,
    \item \textbf{Contributed to modernizing the legacy codebase} by transitioning to React.js.
\end{itemize}
\vspace{0.2em}
\textbf{ Tools Used}: \textit{JavaScript, Backbonejs, Marionette, Reactjs, FlowType, Grunt.js, Karma, Bower Components}

\vspace{1em}

\noindent
\textbf{\Large Weavler AB}, An accessible e-commerce artisans platform (with 1.6M SEK \href{https://pts.se}{\color{blue}PTS} grant) \hfill Stockholm, Sweden\\
\textit{Full Stack Developer} \hfill January 2016 - March 2017
\begin{itemize}
\setlength{\itemsep}{0.5em}
    \item \textbf{Managed AWS cloud infrastructure}, reducing operational costs by 40\%.
    \item \textbf{Integrated services} like Mandrill, Slack bots and PayPal, enhancing platform functionality.
    \textbf{Implemented SEO strategies} with server-side rendering.     \item \textbf{Designed responsive} email templates for email clients and browsers.

    \item \textbf{Created an intelligent notification and chat bot} for onboarding and FAQs.
    \textbf{Developed a open source babel plugin} to quickly implement translations to the entire project.
    \textbf{Enhanced accessibility} with text customization and color filters, aligning with WCAG standards.
    \textbf{Experimented advanced features} like speech synthesis and recognition, improving accessibility.
\end{itemize}
\vspace{0.2em}
\textbf{ Tools Used:} \textit{JavaScript, Express, Reactjs, Alt.js, Accessibility, SSR, MongoDB, Babel Plugin(OSS)}

\vspace{1em}

\noindent
\textbf{\Large Bumbee Labs AB}, \hfill Stockholm, Sweden\\
\textit{Software Engineer Intern (Summer Project)} \hfill July 2015 - September 2015
\begin{itemize}
\setlength{\itemsep}{0.5em}
    \item \textbf{Applied MongoDB aggregation framework} and map-reduce to generate pre-aggregated and structured reports from millions of samples with raw data.
    \item \textbf{Enhanced full-stack dashboard application} with gulp build and assisted implementing Key Performance Indicators.
    \item \textbf{Explored the feasibility of migrating the tech stack} to Reactjs and the Eve Python framework.
\end{itemize}
\vspace{0.2em}
\textbf{ Tools Used:} \textit{MongoDB, AngularJS, Python, Heroku, Laravel (PHP), System Monitoring}

% \textbf{\color{white}
% react
% problem solving
% pipeline
% front end
% data engineer
% continuous learning
% compliance
% communication
% cloud computing
% cloud
% back end
% automated tests
% }

\end{minipage}
