\cventry{Jan 2023 - Dec 2024}
{Senior Software Engineer (24 months)}
{Oneflow AB,  Digital Signature and Contract Management Platform}
{Stockholm \Large\texttwemoji{sweden}}{}
{
  \begin{itemize}[itemsep=0.07pt, topsep=0.5pt]
    \item \textbf{Strategically integrated TypeScript} into a mixed legacy codebase with FlowType and JavaScript, resulting in a 70\% reduction in type-related errors, significantly enhancing code reliability and maintainability.
    Leveraged previously introduced zod's type inference for robust type hinting in business data.
    \item \textbf{Automated the conversion of JavaScript} modules to TypeScript with a custom script preserving version control history, saving over 200+ hours of manual work, accelerating development timelines.
    \item \textbf{Unified distributed ACL permissions} into a single utility module, managing complex contexts and user roles (owner, guest) to simplify maintenance, migration and enhance scalability.
   \end{itemize}
  % \mainTech{
  %   \tech{JavaScript},
  %   \tech{TypeScript},
  %   \tech{Connexion},
  %   \tech{Reactjs},
  %   \tech{Jest},
  %   \tech{Enzyme},
  %   \tech{Testing-library},
  %   \tech{Playwright}
  % }
  % \techStackList{
  %   \tech{MySQL},
  %   \tech{Express.js},
  %   \tech{Flask},
  %   \tech{Python},
  %   \tech{Backbone.js},
  %   \tech{Marionette},
  %   \tech{Webpack},
  %   \tech{Grunt.js}
  % }
}
\cventry{Oct 2021 - Dec 2022}
{Engineering Team Lead (15 months)}
{Oneflow AB}
{Stockholm \Large\texttwemoji{sweden}}{}
{
  \begin{itemize}[itemsep=0.07pt, topsep=0.5pt]
    \item \textbf{Co-led the development of a new JSON-based rich text editor} seamlessly integrating with legacy HTML, increasing user satisfaction by 60\% and providing a modern, cohesive editing experience.
    \item \textbf{Mentored and empowered the development team} to a self-organizing model, overseeing hiring and onboarding while instilling a continuous improvement culture. This resulted in increased productivity, stronger ownership, and scalable team practices.
    \item \textbf{Pioneered an end-to-end testing transformation} with Playwright, starting with an innovative approach to replicate mob testing scenarios. This significantly reduced regressions and boosted efficiency.
    Later, I spearheaded a complete rewrite of the end-to-end testing suite in Playwright.
    \item \textbf{Engineered a lightweight Zod-based data validation library} which streamlined data validation and minimized runtime errors.
  \end{itemize}
}
\cventry{Mar 2019 - Sep 2021}
{Full Stack Integration Engineer (31 months)}
{Oneflow AB}
{Stockholm \Large\texttwemoji{sweden}}{}
{
  \begin{itemize}[itemsep=0.07pt, topsep=0.5pt]
    \item \textbf{Established the Integration Team} from the ground up, creating foundational processes and best practices for long-term scalability, while strategically aligning integration solutions with business needs.
    \item \textbf{Designed multi-client applications} with Python and React.js, facilitating seamless integrations with platforms like HubSpot and SuperOffice, expanding Oneflow’s reach and interoperability.
    \item \textbf{Stabilized and enhanced the Public API}, which enabled a robust third-party integration ecosystem, contributing to client satisfaction and platform versatility.
  \end{itemize}
}
\cventry{Apr 2017 - Feb 2019}
{JavaScript Developer(23 months)}
{Oneflow AB}
{Stockholm \Large\texttwemoji{sweden}}{}
{
  \begin{itemize}[itemsep=0.07pt, topsep=0.5pt]
    \item \textbf{Innovatively Integrated React Router into a Backbone.js-based client} to build Identity and Access Management, facilitate faster prototyping cross-linked user management and efficient testing.
    \item \textbf{Optimized CI build processes}, reducing build times by 40\%,
    \item \textbf{Contributed to modernizing the legacy codebase} by transitioning to React.js.
  \end{itemize}
}
